\section{References}\label{references}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Google DeepMind. 2026. \emph{Gemma 4 model card}.
  \url{https://ai.google.dev/gemma/docs/core/model_card_4}
\item
  Oluwaseyi Feyisetan, Borja Balle, Thomas Drake, and Tom Diethe. 2020.
  \emph{Privacy- and Utility-Preserving Textual Analysis via Calibrated
  Multivariate Perturbations}. Proceedings of WSDM 2020.
  \url{https://dl.acm.org/doi/10.1145/3336191.3371856}
\item
  Xiang Yue, Huseyin A. Inan, Xintao Wu, and Arash Ghasemi. 2021.
  \emph{Differential Privacy for Text Analytics via Natural Text
  Sanitization}. Findings of ACL 2021.
  \url{https://aclanthology.org/2021.findings-acl.337.pdf}
\item
  Justus Mattern, Benjamin Weggenmann, and Florian Kerschbaum. 2022.
  \emph{The Limits of Word Level Differential Privacy}. Findings of
  NAACL 2022. \url{https://aclanthology.org/2022.findings-naacl.65.pdf}
\item
  Sai Chen, Fengran Mo, Yanhao Wang, Cen Chen, Jian-Yun Nie, Chengyu
  Wang, and Jamie Cui. 2023. \emph{A Customized Text Sanitization
  Mechanism with Differential Privacy}. Findings of ACL 2023.
  \url{https://aclanthology.org/2023.findings-acl.355.pdf}
\item
  Ahmed Musa Awon, Yun Lu, Shera Potka, and Alex Thomo. 2025.
  \emph{CluSanT: Differentially Private and Semantically Coherent Text
  Sanitization}. NAACL 2025.
  \url{https://aclanthology.org/2025.naacl-long.187.pdf}
\item
  Juhua Zhang, Zhiliang Tian, Minghang Zhu, Yiping Song, Taishu Sheng,
  Siyi Yang, Qiunan Du, Xinwang Liu, Minlie Huang, and Dongsheng Li.
  2025. \emph{DYNTEXT: Semantic-Aware Dynamic Text Sanitization for
  Privacy-Preserving LLM Inference}. Findings of ACL 2025.
  \url{https://aclanthology.org/2025.findings-acl.1038/}
\item
  Meng Tong, Kejiang Chen, Xiaojian Yuan, Jiayang Liu, Weiming Zhang,
  Nenghai Yu, and Jie Zhang. 2025. \emph{On the Vulnerability of Text
  Sanitization}. NAACL 2025.
  \url{https://aclanthology.org/2025.naacl-long.266.pdf}
\item
  Maximin Coavoux, Shashi Narayan, and Shay B. Cohen. 2018.
  \emph{Privacy-preserving Neural Representations of Text}. EMNLP 2018.
  \url{https://aclanthology.org/D18-1001/}
\item
  Qiongkai Xu, Lizhen Qu, Chenchen Xu, and Ran Cui. 2019.
  \emph{Privacy-Aware Text Rewriting}. INLG 2019.
  \url{https://aclanthology.org/W19-8633.pdf}
\item
  Max Friedrich, Arne Köhn, Gregor Wiedemann, and Chris Biemann. 2019.
  \emph{Adversarial Learning of Privacy-Preserving Text Representations
  for De-Identification of Medical Records}. ACL 2019.
  \url{https://aclanthology.org/P19-1584.pdf}
\item
  Guillaume Lample, Miguel Ballesteros, Sandeep Subramanian, Kazuya
  Kawakami, and Chris Dyer. 2016. \emph{Neural Architectures for Named
  Entity Recognition}. arXiv:1603.01360.
  \url{https://arxiv.org/abs/1603.01360}
\item
  Franck Dernoncourt, Ji Young Lee, Ozlem Uzuner, and Peter Szolovits.
  2017. \emph{De-identification of patient notes with recurrent neural
  networks}. Journal of the American Medical Informatics Association.
  \url{https://pubmed.ncbi.nlm.nih.gov/28040687/}
\item
  Zengjian Liu, Buzhou Tang, Xiaolong Wang, and Qingcai Chen. 2017.
  \emph{De-identification of clinical notes via recurrent neural network
  and conditional random field}. Journal of Biomedical Informatics.
  \url{https://pubmed.ncbi.nlm.nih.gov/28579533/}
\item
  Nicholas Carlini, Florian Tramèr, Eric Wallace, Matthew Jagielski,
  Ariel Herbert-Voss, Katherine Lee, Adam Roberts, Tom Brown, Dawn Song,
  Úlfar Erlingsson, Alina Oprea, and Colin Raffel. 2021.
  \emph{Extracting Training Data from Large Language Models}. USENIX
  Security 2021.
  \url{https://www.usenix.org/conference/usenixsecurity21/presentation/carlini-extracting}
\item
  Fatemehsadat Mireshghallah, Kartik Goyal, Archit Uniyal, Taylor
  Berg-Kirkpatrick, and Reza Shokri. 2022. \emph{Quantifying Privacy
  Risks of Masked Language Models Using Membership Inference Attacks}.
  EMNLP 2022. \url{https://aclanthology.org/2022.emnlp-main.570/}
\item
  Jie Huang, Hanyin Shao, and Kevin Chen-Chuan Chang. 2022. \emph{Are
  Large Pre-Trained Language Models Leaking Your Personal Information?}
  Findings of EMNLP 2022.
  \url{https://aclanthology.org/2022.findings-emnlp.148/}
\item
  Ilya Mironov. 2017. \emph{Rényi Differential Privacy}.
  \url{https://arxiv.org/abs/1702.07476}
\item
  Yu-Xiang Wang, Borja Balle, and Shiva Prasad Kasiviswanathan. 2019.
  \emph{Subsampled Rényi Differential Privacy and Analytical Moments
  Accountant}. AISTATS 2019.
  \url{https://proceedings.mlr.press/v89/wang19b/wang19b.pdf}
\item
  U.S. Department of Health and Human Services. 2025. \emph{Guidance
  Regarding Methods for De-identification of Protected Health
  Information in Accordance with the Health Insurance Portability and
  Accountability Act (HIPAA) Privacy Rule}.
  \url{https://www.hhs.gov/hipaa/for-professionals/special-topics/de-identification/index.html}
\item
  Electronic Code of Federal Regulations. \emph{45 CFR § 164.514 ---
  Other requirements relating to uses and disclosures of protected
  health information}.
  \url{https://www.ecfr.gov/current/title-45/subtitle-A/subchapter-C/part-164/subpart-E/section-164.514}
\end{enumerate}
